A robust DPG method for convection-dominated diffusion problems II: adjoint boundary conditions and mesh-dependent test norms.

### 2013-04-29 docs/Jesse/HeuerPaper/responseForReviewers.tex

%\documentclass[11pt,onecolumn]{scrartcl}
\documentclass{letter}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{letterbib}
\usepackage{tikz}
%\usepackage{subfigure}
\usepackage[normalem]{ulem}

\newcommand{\bs}[1]{\boldsymbol{#1}}
\DeclareMathOperator{\diag}{diag}

\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}

\newcommand{\tablab}[1]{\label{tab:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}

\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\snor}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}

\newcommand{\eval}[2][\right]{\relax
  \ifx#1\right\relax \left.\fi#2#1\rvert}

\def\etal{{\it et al.~}}

\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\tensor}[1]{\underline{\vect{#1}}}
\newcommand{\del}{\Delta}
\newcommand{\grad}{\nabla}
\newcommand{\curl}{\grad \times}
\renewcommand{\div}{\grad \cdot}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\eip}[1]{a\left( #1 \right)}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}

\newcommand{\circone}{\ding{192}}
\newcommand{\circtwo}{\ding{193}}
\newcommand{\circthree}{\ding{194}}
\newcommand{\circfour}{\ding{195}}
\newcommand{\circfive}{\ding{196}}

\def\arr#1#2#3#4{\left[
\begin{array}{cc}
#1 & #2\\
#3 & #4\\
\end{array}
\right]}
\def\vecttwo#1#2{\left[
\begin{array}{c}
#1\\
#2\\
\end{array}
\right]}
\def\vectthree#1#2#3{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
\end{array}
\right]}
\def\vectfour#1#2#3#4{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
#4\\
\end{array}
\right]}

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\G} {\Gamma}
\newcommand{\Gin} {\Gamma_{in}}
\newcommand{\Gout} {\Gamma_{out}}

\signature{Jesse Chan, Norbert Heuer, Tan Bui-Thanh, and Leszek Demkowicz}
\address{201 East 24th St, Stop C0200\\
Austin, Texas 78712-1229}
\begin{document}
\begin{letter}{Dr Alexey Chernov\\CAMWA Guest Editor\\Special Issue: HONAPDE 2012}

%\tableofcontents
%\maketitle

\opening{Dear Dr Chernov,}

The authors are very grateful for the feedback, comments and suggestions provided by both reviewers.  Please accept the attached revised version of our paper:

\begin{center}
Jesse Chan, Norbert Heuer, Tan Bui-Thanh, and Leszek Demkowicz\\
\textit{A robust DPG method for convection-dominated diffusion problems II: adjoint boundary conditions and mesh-dependent test norms.}
\end{center}

In addition to the changes requested by the reviewers, we have made a few additional corrections in the manuscript.  The title has been changed to match the submitted title, and a citation has been added in Section 1.4 for Dr Wolfgang Dahmen's work, which we discovered after submission.  His work is equivalent to the DPG method for alternative variational formulations.  Additionally, the following changes have been made to the manuscript
\begin{enumerate}
\item On page 2, the SUPG method is mentioned to be $H^1$ optimal.  We have added the specification ``in the 1D case", as this claim does not hold in 2 and 3 dimensions.
\item We have removed part of Section 1.5, previously titled ``Canonical energy norm pairings for the ultra-weak formulation".  Previously, the quasi-optimal/graph test norm was stated to induce a norm on the trial space $U$ of a specific form; it was discovered that this proof was incorrect, and the exact form of the induced energy norm under the graph test norm is unknown.  The section has been rewritten to correct this.  Figure 1 was also removed.  
\item In Section 2 near the second half of page 8, we have changed the description of the broken $H^1\times H({\rm div})$ test norm to be the ``canonical norm on this test space" as opposed to simply ``the canonical test norm", which could be confused with the \textit{quasi-optimal/graph test norm} described as the canonical norm in the previous section.  
\item In Section 3.5, in replacing the image with a higher quality eps version, we plot a solution to the 1D adjoint equation with a given load.  The function plotted was inconsistent with the load described; this is fixed.  
\item In Section 4.1 and onwards, some images have been replaced with higher quality image files.  A typo is corrected on p24, concerning the greedy adaptive strategy used (we refine elements who satisfy $e_K^2 \leq \alpha^2 \max e_K^2$, but had neglected to square the factor $\alpha$ in the original manuscript).

\end{enumerate}

We thank the reviewers for their insightful comments, recommendations, and favorable reviews.  Attached are details on the revisions made as requested from each reviewer, as well as the authors responses to each revision request.

\textbf{Reviewer 1}

%The paper is concerned with DGP methods applied to linear convection-diffusion equations in the small-diffusion limit for the inflow boundary conditions of [13]. The authors identify a non-canonical and mesh-dependent test norm, which is explicitly computable and uniformly equivalent to the energy norm (cf. Lemma 1). The performance of the methods is then tested in a set of numerical examples using h-adaptivity. The tests confirm the robustness of the methods, as expected. Additionally, it is observed that the ratios of $L^2$ errors and energy errors are uniformly bounded in the Peclet number.
%
%Assessment:
%DGP methods have emerged as robust discretization methods for convection-diffusion problems (as well as for other singularly perturbed problems). They are based on the local computation of so-called optimal test functions, which by construction yield stability and quasi-optimality in the norms considered. In this paper, DGP methods are extended to the inflow conditions of [13] while earlier papers address only Dirichlet conditions. It turns out that the effects of the different boundary conditions may be quite dramatic due to the different structure of the adjoint problems, and indeed require different test norms, as illustrated in Section 3.5. As such, this is an interesting contribution to the theory of DGP methods.

%Although I didn't check all details, the results of the paper appear correct and new. The paper is well written; its introduction also nicely surveys the main ideas of DGP methods. I recommend the paper for publication in CAMWA.

%However, I would like to authors to address the following minor suggestions/comments/typos:
\begin{enumerate}
\item \textcolor{red}{After equation (1): $U$ should be $U_h$.}  Corrected.

\item \textcolor{red}{Page 7, last line: A period is missing at the end of the last sentence.}   We fixed the issue on equation (10), where there was a comma instead of a period, but I could not find this typo.

\item \textcolor{red}{The new boundary conditions should be discussed in a few more details. What do they model physically? What happens on $\Gamma_0$? Discussion of weak formulation and well-posedness of the continuous problem?}.  Certainly - we've added a short explanation.  In summary, the boundary condition models physically the conserved flux corresponding to the conservation law.  However, though the boundary condition holds physical meaning, this boundary condition is chosen instead because it approximates, for small enough $\epsilon$ and $\beta_n > 0$ on $\Gamma_0$, the standard boundary condition $u = u_0$ on $\Gamma_0$.

Due to the nature of the ultra-weak variational formulation, the weak formulation for both standard boundary conditions on $u$ and the new boundary condition on $\Gamma_0$ are the same.  For convection-diffusion, the variational form is
\[
b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{v,\tau}} = \LRa{\fnh,v} - \LRa{\uh,\tau_n} + \text{field/interior terms}
\]

The application of boundary conditions is equivalent to the imposition of a natural boundary condition in both cases, where either $\LRa{\fnh,v}_{\Gamma_0}$ or $\LRa{\uh,\tau_n}_{\Gamma_0}$ are given data and become forcing terms.

Regarding the well-posedness of the variational problem, we refer the reviewer to \cite{analysisDPG}, whose analysis also covers the case of these boundary conditions (assuming well-posedness of the continuous problem), or \cite{Bui-ThanhDemkowiczGhattas11b}, where both the standard inflow boundary condition on $u$ and the proposed Robin boundary condition can be analyzed in the framework of Friedrichs systems.

Regarding the well-posedness of the continuous problem, we refer the reviewer to \cite{Hesthaven96astable}, the paper of Dr Jan Hesthaven, where he proves well-posedness of both the transient case and the case as $\epsilon \rightarrow 0$.

\item \textcolor{red}{Page 10, mid page: There is a latex error regarding the reference to Figure 2, and the label in Figure 2 needs to be fixed.}  Corrected.

\item \textcolor{red}{Page 12: Several sentences are in boldface, for no obvious reasons. This should be changed. }  Corrected.

\item \textcolor{red}{Assumptions (19)-(21): It should be discussed how restrictive these assumptions are.} Corrected; a footnote has been added discussing the physical interpretation of such assumptions.

A few comments on the assumptions: 
\begin{enumerate}
\item These assumptions are only sufficient conditions - these conditions have been introduced only to ensure a robust bound exists for solutions to the adjoint equations.  For example, the condition $\div \beta = 0$ is only a sufficient condition to ensure the well-posedness of an auxiliary problem related to the proof of a lemma.  The lemma can still hold without this condition
\item These assumptions are strictly for the steady-state case with no first-order term.  In the case when there is a first-order term, it is easy to prove Lemma 3 without the aid of the condition $\curl \beta = 0$.  
\item Several numerical experiments (to be reported in an upcoming report on locally-conservative DPG) do not indicate a loss of robustness even when these conditions are violated.  For example, experiments with the viscous Burgers' equation 
\[
u_{,t} + \LRp{\frac{u^2}{2}}_{,x} - \epsilon \nabla u = 0
\]
yield a solution with a shock from $(x,y) = (.5,.5)$ to $(.5,1)$ for initial condition $u(x,0) = 1-2x$.  The linearized equation is a convection-diffusion equation with $\beta = (u,1)$.  When $u$ has a shock, $\grad \beta + \grad \beta^T - \div \beta I = O(\epsilon^{-1})$, and condition (19) is violated, but there was no observable degeneration in solution quality as $\epsilon$ decreased.  
\end{enumerate}

\item \textcolor{red}{Page 15, last line: change "proper" to "these", "the robust bounds" to "the following robust bounds".}  Corrected.

\item \textcolor{red}{Lemma 1: the equivalence bounds appear not be p-robust. These should be mentioned explicitly in the statement of the lemma.}  The bounds in Lemma 1 should hold under any mesh and arbitrary $p$ - there were only regularity assumptions made in the proof.  Could we request a more detailed explanation into why the bounds appear to not be $p$-robust?

\item \textcolor{red}{Shouldn't the curves in Figure 8 (left) be on top of each other to indicate robustness? Please comment. Also: Please indicate the orders of the convergence which are observed?} Noted - we have expanded the paragraph discussing Figures 7 and 11, (the figures have been renumbered).

As both reviewers have expressed concern over the ratio curves in Figure 8, I have discussed this in a section at the end of this letter explaining the interpretation of the ratio curves for various values of $\epsilon$.

Concerning the orders of convergence - 
\begin{enumerate}
\item We are mostly in the pre-asymptotic range for most of our problems, and thus do not expect to observe optimal rates in our setup for small values of $\epsilon$.  For this reason, we believe that reporting convergence rates would not add much meaningful information.  
\item We have verified that we do indeed achieve optimal rates asymptotically under uniform refinements for $\epsilon = 1$, $1e-1$, and $1e-2$.  However, the mesh size at which the optimal rate is achieved becomes smaller and smaller as $\epsilon$ shrinks; we reach the optimal rate immediately for $\epsilon = 1$, but for $\epsilon = 1e-2$, our rates of convergence between $h = 1/128$ and $h = 256$ changed from 2.5255 to 2.8292.  We expect an optimal rate of $3$, but as this example shows, it may not be computationally feasible to get to that asymptotic range and demonstrate robustness for very small $\epsilon$ at the same time.  
\item Adaptivity should restore the optimal rate of convergence with respect to degrees of freedom; however, for strongly anisotropic solutions (such as boundary layer solutions), this optimal rate is achieved only through the use of anisotropic refinements, which we have not yet implemented.  
\end{enumerate}

\item \textcolor{red}{Page 24: How is the estimator $e_K^2$ defined? Please provide some details.}  Corrected.

Specifically, at the top of page 5, a paragraph is dedicated to the definition of the \textit{error representation function}, which is the inverse Riesz image of the residual of the variational equation (in $V'$) - in other words, the solution of
\[
(e,\delta v)_V = l(\delta v) - b(u_h,\delta v), \quad \forall v\in V.
\]
Under this, $\nor{e}_V = \nor{Bu-Bu_h}_{V'} = \nor{u-u_h}_E$ - the norm of the error representation function returns the norm of the error in the energy norm.  We note that, under a localizable norm and discontinuous test basis, this error representation function can be computed locally and used as a local error indicator.  $e_K^2$ is defined to be the squared energy norm of the error representation function over a single element $\nor{e}_{V(K)}^2$.  Summing together these elementwise contributions recovers the actual squared energy error over the domain.

\end{enumerate}

\textbf{Reviewer 2}

%The authors continue the analysis of the Discontinuous Petrov-Galerkin method for a singularly perturbed convection-diffusion problem initiated in [10].  The paper starts with an introduction to the abstract setting of the DPG. The core of the paper studies the DPG for the (scalar) convection-diffusion problem. Two issues are studied: first, the choice of the norm on the test space and second the impact of this choice on the ``energy norm", i.e., the norm on the trial space. The norm on the test space should fulfill several requirements: firstly, it should be localizable so that the test functions (which have to be computed) can be computed locally and secondly it should avoid test functions that have boundary layers, which are difficult to resolve. In this paper, these two issues are addressed by using the mesh-dependent norm given in Lemma 1 on p. 17. Lemma 1 also shows that the ``energy norm" induced by this norm on the test space allows for control of the field variables, in particular, the primal variable u.
%
%The paper reads very well, is of topical interest and very well suited for CAMWA. The referee recommends publication after the following issues are addressed.

\begin{enumerate}
\item \textcolor{red}{The authors are encouraged to carefully proof-read the proof of Lemma 1.}  Noted.  Shortly after submitting, the authors did go through the proof of Lemma 1 again with a careful read-through.
\item \textcolor{red}{The notation $\nor{\cdot}_{V,K}$ is used in the proof of Lemma 1 repeatedly and the referee did not find a definition.}  Corrected.  The definition of $\nor{\cdot}_{V,K}$ is included on the end of page 4 in the footnote on localizable norms, as well as on p18, right before the definition is used.  Additionally, to be consistent with the notation $L^2(K)$, we have changed the notation from $\nor{\cdot}_{V,K}$ to $\nor{\cdot}_{V(K)}$ 
\item \textcolor{red}{Towards the end of the proof of Lemma 1, the notation $\nor{\eta} + \nor{w}$ appears. The context suggest that $\eta$ and $w$ are measured in the $L^2$-norm, but $H^1$ and $H({\rm div})$ seem more likely from the context.}  Corrected.  The reviewer is correct, the proper setting was indeed $H^1$/$H({\rm div})$.  
\item \textcolor{red}{The numerical results show an $\epsilon$-dependence in the approximation (cf. Figs. 8, 10, 12) although the error measure is rather weak (the $L^2$-norm of the field variable $u$ doesn't ``see" the boundary layer). The referee feels that the readers would appreciate some comments.}  Additional comments describing the ratios have been added on p25.  Figure 10 (now Figure 9) largely addresses the issue of modeling error in the inflow condition.

As both reviewers have expressed concern over the ratio curves in Figure 8, please see the section below on the interpretation of the ratio curves for various values of $\epsilon$.

### 2013-04-29 docs/Jesse/HeuerPaper/paperForCAMWA.tex
updating heuer paper

%&pdflatex
\documentclass[11pt,onecolumn]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage[normalem]{ulem}

@@

%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
\title{Robust DPG method for convection-dominated diffusion problems II: a natural inflow condition}
\date{}
\begin{document}

@@

Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization techniques.  Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.  The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.  SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.  An important difference between residual-based stabilization techniques and other stabilizations is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).\footnote{Contrast this to an artificial diffusion method, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters. The exact solution to the original equation no longer satisfies the new stabilized formulation.}

The addition of residual-based stabilization terms can also be interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.  We approach the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.

@@

Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces. Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets. We are interested in the following problem  
\begin{equation}
\eqnlab{variationEq}
\left\{
  \begin{array}{l}
    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
  \end{array}
  \right.
\end{equation}
where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
bilinear form.  $U$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.

@@

Since $U_h \subset U$ is spanned by a finite number of basis functions $\LRc{\varphi_i}_{i=1}^N$, \eqnref{optv} allows us to compute (for each basis function) a corresponding optimal test function $v_{\varphi_i}$. The collection $\LRc{v_{\varphi_i}}_{i = 1}^N$ of optimal test functions then forms a basis for the optimal test space.  In order to express optimal test functions defined in \eqnref{optv} in a more familiar form, we take  $\delta u = \varphi$, a generic basis function in $U_h$, and rewrite \eqnref{optv} as
\[
R_Vv_{\varphi} = B\varphi, \quad \text{in } V',
\]
which is, by definition, equivalent to
\[
\LRp{v_\varphi,\delta v}_V = \LRa{R_Vv_\varphi,\delta v}_{V}=
\LRa{B\varphi, \delta v}_V = b\LRp{\varphi,\delta v}, \quad
\forall \delta v \in V.
\]
%% Now, let us define the \textit{trial-to-test} operator $T =
%% R_V^{-1}B$, which, by \eqnref{optv}, maps a trial function $\delta u$
%% to its corresponding \textit{optimal} test function $v = T\delta u$.
%% On the other hand,
As a result, optimal test functions can be determined by solving the auxiliary
variational problem
\begin{equation}
\eqnlab{optvVar}
\left(v_\varphi,\delta v\right)_V = b(\varphi,\delta v), \quad \forall
\delta v \in V.
\end{equation}
However, in general, for standard $H^1$ and $H({\rm div})$-conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function requires a global operation over the entire mesh, rendering the method impractical. A breakthrough came through the development of
discontinous Galerkin (DG) methods, for which basis functions are
discontinuous over elements. In particular, the use of discontinuous
test functions $\delta v$ reduces the problem of determining global 
optimal test functions
in \eqnref{optvVar} to local problems that can be solved in an
element-by-element fashion.

@@

It is now well known that the DPG method
delivers the best approximation error in the ``energy norm" --- that is
\cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
\begin{equation}
\eqnlab{optimalError}
\nor{u-u_h}_{U,E} = \inf_{w\in U_h} \nor{u-w}_{U,E},
\end{equation}
where the energy norm $\|\cdot \|_{U,E}$ is defined for a function $\varphi \in U$ as
\begin{equation}
\eqnlab{energyNorm} \|\varphi\|_{U,E} \coloneqq \sup_{v\in V}
\frac{b(\varphi,v)}{\|v\|_V} = \sup_{\nor{v}_V = 1} b(\varphi,v) =
\sup_{\nor{v}_V = 1} \LRa{B\varphi,v}_V = \nor{B\varphi}_{V'} =
\nor{v_\varphi}_V,
\end{equation}
where the last equality holds due to the isometry of the Riesz map
$R_V$ (or directly from \eqnref{optvVar} by taking the supremum). An
additional consequence of adopting such an energy norm is that,
without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}$ can
be determined by computing $\|v_{u-u_h}\|_V$ from the following
identity
\[
\left(v_{u-u_h},\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta
v} - b(u_h,\delta v).
\]
This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the  residual in $V'$.

@@

\subsection{Duality between trial and test norms (energy norm pairings)}
%\subsection{Abstract energy norm pairings}
\seclab{energyPair}
A clear property of the energy norm defined by \eqnref{energyNorm} is that the trial norm $\nor{\cdot}_{U,E}$ is induced by a given test norm. However, the reverse relationship holds as well; for any trial norm, the test norm that induces such a norm is recoverable through duality. We have a result, proved in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
\[
\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{w,v}}{\nor{v}_{V,U}}.
\]
where $\nor{v}_{V,U}$ is defined through
\[
\nor{v}_{V,U} = \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U}}.
\]
%In other words, the norm $\nor{\cdot}_V$ in $V$ can be recovered using the energy norm $\nor{\cdot}_{U,E}$ in $U$, and vice versa.

@@

The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries. There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}.

@@

%\subsection{Optimal and quasi-optimal test norms}
\subsection{Canonical energy norm pairings for ultra-weak formulation}

>>>>

%&pdflatex
\documentclass[11pt,onecolumn]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage[normalem]{ulem}
\usepackage{epstopdf}

@@

%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
\title{A robust DPG method for convection-dominated diffusion problems II: adjoint boundary conditions and mesh-dependent test norms.}
\date{}
\begin{document}

@@

Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization techniques.  Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.  The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.  In the 1D case, SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.  An important difference between residual-based stabilization techniques and other stabilizations is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).\footnote{Contrast this to an artificial diffusion method, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters. The exact solution to the original equation no longer satisfies the new stabilized formulation.}

The addition of residual-based stabilization terms has also been interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.  We approach the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.

@@

Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces. Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets. We are interested in the following problem  
\begin{equation}
\eqnlab{variationEq}
\left\{
  \begin{array}{l}
    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
  \end{array}
  \right.
\end{equation}
where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
bilinear form.  $U_h$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.

@@

Since $U_h \subset U$ is spanned by a finite number of basis functions $\LRc{\varphi_i}_{i=1}^N$, \eqnref{optv} allows us to compute (for each basis function) a corresponding optimal test function $v_{\varphi_i}$. The collection $\LRc{v_{\varphi_i}}_{i = 1}^N$ of optimal test functions then forms a basis for the optimal test space.  In order to express optimal test functions defined in \eqnref{optv} in a more familiar form, we take  $\delta u = \varphi$, a generic basis function in $U_h$, and rewrite \eqnref{optv} as
\[
R_Vv_{\varphi} = B\varphi, \quad \text{in } V',
\]
which is, by definition, equivalent to
\[
\LRp{v_\varphi,\delta v}_V = \LRa{R_Vv_\varphi,\delta v}_{V}=
\LRa{B\varphi, \delta v}_V = b\LRp{\varphi,\delta v}, \quad
\forall \delta v \in V.
\]
%% Now, let us define the \textit{trial-to-test} operator $T =
%% R_V^{-1}B$, which, by \eqnref{optv}, maps a trial function $\delta u$
%% to its corresponding \textit{optimal} test function $v = T\delta u$.
%% On the other hand,
As a result, optimal test functions can be determined by solving the auxiliary
variational problem
\begin{equation}
\eqnlab{optvVar}
\left(v_\varphi,\delta v\right)_V = b(\varphi,\delta v), \quad \forall
\delta v \in V.
\end{equation}
However, in general, for standard $H^1$ and $H({\rm div})$-conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function requires a global operation over the entire mesh, rendering the method impractical. A breakthrough came through the development of discontinous Galerkin (DG) methods, for which basis functions are discontinuous over elements. In particular, the use of discontinuous test functions $\delta v$ and a \textit{localizable} norm $\nor{\cdot}_V$\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form 
$$\nor{v}_{V(\Oh)}^2 = \sum_{K\in\Oh} \nor{v}_{V(K)}^2,$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} reduces the problem of determining global optimal test functions in \eqnref{optvVar} to local problems that can be solved in an element-by-element fashion.

@@

It is now well known that the DPG method delivers the best approximation error in the ``energy norm" --- that is \cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
\begin{equation}
\eqnlab{optimalError}
\nor{u-u_h}_{U,E} = \inf_{w\in U_h} \nor{u-w}_{U,E},
\end{equation}
where the energy norm $\|\cdot \|_{U,E}$ is defined for a function $\varphi \in U$ as
\begin{equation}
\eqnlab{energyNorm} \|\varphi\|_{U,E} \coloneqq \sup_{v\in V}
\frac{b(\varphi,v)}{\|v\|_V} = \sup_{\nor{v}_V = 1} b(\varphi,v) =
\sup_{\nor{v}_V = 1} \LRa{B\varphi,v}_V = \nor{B\varphi}_{V'} =
\nor{v_\varphi}_V,
\end{equation}
where the last equality holds due to the isometry of the Riesz map
$R_V$ (or directly from \eqnref{optvVar} by taking the supremum). An
additional consequence of adopting such an energy norm is that,
without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}  = \nor{Bu - Bu_h}_{V'} = \nor{R_V^{-1}\LRp{l-Bu_h}}_{V}$ can
be determined by computing the \textit{error representation function} $e \coloneqq R_V^{-1}\LRp{l-Bu_h}$ through
\[
\left(e,\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta v} - b(u_h,\delta v)
\]
and measuring its norm $\|e\|_V$.  This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the residual in $V'$.  Under the assumption of a localizable norm on $V$, we can compute the squared norm over the entire domain $\nor{e}_{V(\Oh)}^2$ as the sum of individual element contributions $\sum_{K\in \Oh} \nor{e}_{V(K)}^2$.  We define $e_K^2 \coloneqq \nor{e}_{V(K)}^2$ as a local error indicator with which we can drive adaptive mesh refinement.

@@

\subsection{Duality between trial and test norms (energy norm pairings)}
%\subsection{Abstract energy norm pairings}
\seclab{energyPair}
A clear property of the energy norm defined by \eqnref{energyNorm} is that the trial norm $\nor{\cdot}_{U,E}$ is induced by a given test norm. However, the reverse relationship holds as well; for any trial norm, the test norm that induces such a norm is recoverable through duality. We have a result, Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite\footnote{By definite, we mean that \begin{align*}b(u,v) &= 0, \forall v\in V \Rightarrow u = 0\\ b(u,v)&=0, \forall u\in U \Rightarrow v = 0,\end{align*}  which imply injectivity of the bilinear operator $B$ and its transpose $B'$, defined such that $\LRa{Bu,v} = \LRa{u,B'v}$.  These conditions imply solvability of the variational problem.}, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
\[
\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{w,v}}{\nor{v}_{V,U}}.
\]
where $\nor{v}_{V,U}$ is defined through
\[
\nor{v}_{V,U} = \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U}}.
\]
%In other words, the norm $\nor{\cdot}_V$ in $V$ can be recovered using the energy norm $\nor{\cdot}_{U,E}$ in $U$, and vice versa.

@@

The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries. There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}. Additionally, Cohen, Dahmen and Welper simultaneously extend the minimum residual concept behind DPG to general variational settings and avoid the use of discontinuous test functions by formulating the minimum residual method as a saddle-point problem \cite{DahmenVariationalStabilization}.

@@

%\subsection{Optimal and quasi-optimal test norms}
\subsection{A canonical energy norm pairing for ultra-weak formulation}
